The Increased Effect of Elections and Changing Prime Ministers on Topics Discussed in the Australian Federal Parliament between 1901 and 2018

### 2019-10-30 outputs/docs/paper/paper_MA_structure_edit.Rmd
edits to data section

The remainder of the paper is structured as follows XX

@@

Following the example of the UK a daily text record called Hansard of what was said in the Australian Federal Parliament has been made available since Federation in 1901.[^Verbatimfootnote] Analysing Hansard records and their equivalents is increasingly viable as new methods and reduced computational costs make it easier.

[^Verbatimfootnote]: While Hansard is not necessarily verbatim, it is considered close enough for text-as-data purposes. For instance, @Mollin2008 found that in the case of the UK Hansard the differences would only affect specialised linguistic analysis. @Edwards2016 examined Australia, New Zealand and the UK, and found that changes were usually made by those responsible for creating the Hansard record, instead of the parliamentarians. As those who create Hansard are tasked with creating an accurate record of proceedings, this suggests the records should be fit for the purpose of our analysis.

The recent digitisation of the Canadian Hansard, @BeelenEtc2017, has allowed increased analysis of Canadian parliament text records. For instance, @RheaultCochran2018 examined ideology and party polarisation in Britain and Canada using word embeddings. A digitised version of the UK Hansard has been available for some time. For instance, @Duthie2016 examined which politicians made supportive or aggressive statements toward other politicians, and @PetersonSpirling2018 examined polarisation. One exciting aspect of research using the UK Hansard has been linking text records with other datasets. For instance, @SlapinKirklandLazzaroLeslie2018 linked votes and speeches to examine grandstanding within parties. Another exciting aspect is that as digitisation methods improve, increasingly older UK records can be analysed, for instance, @Dimitruk2018 considered the effect of estate bills on prorogations in seventeenth century England. In New Zealand, @Curran2018 modelled the topics discussed between 2003 and 2016, and @Graham2016 examined unparliamentary language between 1890 and 1950.

Parts of Australian Hansard records have been analysed for various purposes and our paper contributes to a small but growing literature. For instance, @Rasiah2010 examined Hansard records for the Australian House of Representatives to examine whether politicians attempted to evade questions about Iraq during February and March 2003. @GansLeigh2012 examined Australian Hansard records to associate mentions by politicians of certain public intellectuals with neutral or positive sentiment. @Salisbury2011 examined unparliamentary behaviour. And @FraussenGrahamHalpin2019 examined Australian Hansard records to assess the prominence of interest groups. The closest research to ours that we have found is @Boulous2013 who examined parliamentary debate in Australia between 1946 and 2012.

The Australian Federal Parliament makes daily Hansard records available online as PDFs and these are considered the official release. Although we do not use them here, XML records are also available in most cases.[^XMLfootnote] We provide an example of a Hansard PDF page in Appendix \@ref(examplehansardpage). There are 14,680 days of publicly available Hansard records across the two chambers of the Australian Federal Parliament for which we have PDFs and further summary statistics for this are provided in Appendix \@ref(hansardsummarystatistics). Our data cleaning process indicates concerns with a small number of PDFs and these are detailed in Appendix \@ref(knownhansardissues).

[^XMLfootnote]: Tim Sherratt makes Commonwealth XML records for 1901 to 1980 available as a single download at: http://historichansard.net/. Commonwealth XML records from 1998 to 2014 are available from Andrew Turpin’s website, and from 2006 through to today from Open Australia’s website. The records can also be downloaded from the Australian Hansard website or the website can be scraped. We do not use the XML records or scrape the website for this paper because those records are known to be incomplete but the extent of how incomplete they are is unknown. The trade-off for a more-complete record is the errors introduced by having to parse the PDFs.

We use the official PDF release and the formatting of the Hansard records changes over time. We use scripts written in R [@R2018] to convert the PDFs into daily text records.[^scriptsfootnote] Some error is introduced at this stage because many of the records are in a two-column format that need to be separated, and the PDF parsing is not always accurate, especially for older records. An example of the latter issue is that 'the' is often parsed as 'thc'. These errors are corrected when they can be identified, but as there are almost a billion words in the dataset, we are restricted to changes that can be made at scale.

@@

The percentage of stop-words each day is reasonably consistent over time (see Appendix \@ref(stopwordsgraph)). This suggests that the data are fit-for-purpose, although manual inspection does suggest there is some improvement in quality over time. We use Hansard records on a daily basis in this paper, and we pre-process our text before applying a topic model. The specific steps that we take are to: remove numbers and punctuation; change the words to lower case; and concatenate multi-word names titles and phrases, such as new south wales to new_south_wales. Then the sentences are de-constructed and each word considered individually. We do not stem the words because, following @SchofieldMimno2016, we were not able to see much appreciable benefit. The resulting dataset used for analysis contains counts of words by day for 14,680 sitting days between 1901 and 2018.[^datasourcefootnote]

[^datasourcefootnote]: Our dataset is available at: https://github.com/RohanAlexander/hansard. While we are making our data public in an attempt to help other researchers, we cleaned the dataset toward the requirements of this paper. If you have different requirements or have suggestions for how we can improve the dataset for other uses please contact us.

>>>>

The remainder of the paper is structured as follows XX.

@@

The first step is to construct a dataset drived from the Australian Hansard, which contains the text of what was said throughout history in the Australian Federal Parliament. This section gives on the availability and characteristics of such data and outlines the method and steps undertaken to create a ready-to-analyse dataset.

## Background

The term 'Hansard' refers to a daily text record of what was said in parliament. The UK, Australia and Canada all have a Hansard, which span historical periods right up to present day. Following the example of other countries, the Hansard for the Australian Federal Parliament has been made available since Federation in 1901. Analysing Hansard records and their equivalents is increasingly viable as new methods and reduced computational costs make it easier. While Hansard is not necessarily verbatim, it is considered close enough for text-as-data purposes. For instance, @Mollin2008 found that in the case of the UK Hansard the differences would only affect specialised linguistic analysis. @Edwards2016 examined Australia, New Zealand and the UK, and found that changes were usually made by those responsible for creating the Hansard record, instead of the parliamentarians. As those who create Hansard are tasked with creating an accurate record of proceedings, this suggests the records should be fit for the purpose of our analysis.

The recent digitisation of Hansard records has allowed increased analysis of parliament text records. For instance, @RheaultCochran2018 examined ideology and party polarisation in Britain and Canada using word embeddings. In the UK, @Duthie2016 examined which politicians made supportive or aggressive statements toward other politicians, and @PetersonSpirling2018 examined polarisation. One exciting aspect of research using the UK Hansard has been linking text records with other datasets. For instance, @SlapinKirklandLazzaroLeslie2018 linked votes and speeches to examine grandstanding within parties. As digitisation methods improve, increasingly older UK records can be analysed, for instance, @Dimitruk2018 considered the effect of estate bills on prorogations in seventeenth century England. In New Zealand, @Curran2018 modelled the topics discussed between 2003 and 2016, and @Graham2016 examined unparliamentary language between 1890 and 1950.

Parts of Australian Hansard records have been analysed for various purposes and our paper contributes to a small but growing literature. For instance, @Rasiah2010 examined Hansard records for the Australian House of Representatives to examine whether politicians attempted to evade questions about Iraq during February and March 2003. @GansLeigh2012 examined Australian Hansard records to associate mentions by politicians of certain public intellectuals with neutral or positive sentiment. @Salisbury2011 examined unparliamentary behaviour. And @FraussenGrahamHalpin2019 examined Australian Hansard records to assess the prominence of interest groups. The closest research to ours that we have found is @Boulous2013 who examined parliamentary debate in Australia between 1946 and 2012. To our knowledge, this is the first paper that analyses the complete Hansard record since 1901.

## Creation of Hansard dataset

The Australian Federal Parliament makes daily Hansard records available online as PDFs and these are considered the official release.[^XMLfootnote] We provide an example of a Hansard PDF page in Appendix \@ref(examplehansardpage). There are XX PDF files that cover the Hansard over the entire period 1901-2018. Our goal is to take these PDFs and convert them into a digitized dataset of text that is able to be analysed.

[^XMLfootnote]: Although we do not use them here, XML records are also available in most cases. Tim Sherratt makes Commonwealth XML records for 1901 to 1980 available as a single download at: http://historichansard.net/. Commonwealth XML records from 1998 to 2014 are available from Andrew Turpin’s website, and from 2006 through to today from Open Australia’s website. The records can also be downloaded from the Australian Hansard website or the website can be scraped. We do not use the XML records or scrape the website for this paper because those records are known to be incomplete but the extent of how incomplete they are is unknown. The trade-off for a more-complete record is the errors introduced by having to parse the PDFs.

The creation of the Hansard dataset involves the following steps. Firstly, optical character recognition (OCR) is used to convert static PDFs into digitised text. This creates a text file for each PDF with a single character string. Secondly, as many of the original PDFs contained two columns per page, the text file is reshuffled to ensure the text is in the right order. Thirdly, the text is split out such that it is separated by speaker. This involves XX. Lastly, the dataset is created in tidy format (XX REF here), such that there are columns for speaker, the date, and the text of what was said, and every row refers to a different speaker. XX could add more detail to this paragraph XX

These steps were performed using R [@R2018].[^scriptsfootnote] Some error is introduced at this stage because many of the records are in a two-column format that need to be separated, and the PDF parsing is not always accurate, especially for older records. An example of the latter issue is that 'the' is often parsed as 'thc'. These errors are corrected when they can be identified, but as there are almost a billion words in the dataset, we are restricted to changes that can be made at scale.

@@

There are 14,680 days of publicly available Hansard records across the two chambers of the Australian Federal Parliament for which we have PDFs. Further summary statistics for this are provided in Appendix \@ref(hansardsummarystatistics). In general, the frequency of sitting days based on information from the Hansard dataset compared to the actual number of sitting days is comparable, almost complete coverage of our dataset. XX MAYBE pull out a few more summary stats here XX

Our data cleaning process indicates concerns with a small number of PDFs and these are detailed in Appendix \@ref(knownhansardissues). The percentage of stop-words each day is reasonably consistent over time (see Appendix \@ref(stopwordsgraph)). This suggests that the data are fit-for-purpose, although manual inspection does suggest there is some improvement in quality over time.

## Creation of analysis dataset

Using the Hansard dataset, we pre-process the text to create an analysis dataset to model topics and to subsequently investigate the relationship between topics and events. The specific steps that we take are to: remove numbers and punctuation; change the words to lower case; and concatenate multi-word names titles and phrases, such as new south wales to new_south_wales. Then the sentences are de-constructed and each word considered individually. We do not stem the words because, following @SchofieldMimno2016, we were not able to see much appreciable benefit. The resulting dataset used for analysis contains counts of words by day for 14,680 sitting days between 1901 and 2018.[^datasourcefootnote]

[^datasourcefootnote]: Our dataset is available at: https://github.com/RohanAlexander/hansard. While we are making our data public in an attempt to help other researchers, we cleaned the dataset toward the requirements of this paper.
